Democracy, Public Support, and Measurement Uncertainty

### 2021-08-13 paper/dcpo_demsupport.Rmd
split off and cache data-input chunk for speed; use less-intrusive section headers

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: FALSE
    latex_engine: xelatex

@@

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 12pt
indent: true
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
---

@@

There are many plausible explanations for these null results, both theoretical and methodological.
From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes.
Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].

@@

# Theme setup
theme_set(theme_minimal())

# Data input

@@

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propogate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].

As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, intergrating over the uncertainty in latent variables $\theta$ (P A-15).
More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.

>>>>

---
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: FALSE
    number_sections: FALSE
    latex_engine: xelatex

@@

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 12pt
indent: true
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
      - \usepackage{titlesec}
      - \titleformat*{\section}{\normalsize\bfseries}
      - \titleformat*{\subsection}{\normalsize\itshape}
---

@@

There are many plausible explanations for these null results, both theoretical and methodological.
From a theoretical perspective, the effect of democracy on public support may depend not on its mere existence but on its effectiveness [see @Magalhaes2014] and particularly with regard to redistribution [see @Krieckhaus2014].
Similarly, the impact of public support on democracy may depend on the extent to which those who support democracy are also dissatisfied with the current regime's performance; that is, that it is not democratic support that is important to democratic change, but rather unsatisfied democratic demand [see @Qi2011].
_Whether the public support has a pro-democratic or anti-authoritarian effect is also bounded by the emancipative value that, as a belief-anchored orientation, shapes the public's understanding of democracy [see @Brunkert2019; @Kirsch2019; @Kruse2019].
Moreover, the cultural and historical attributes of the emancipative value decide that it cannot be shifted shortly by institutional changes._
Of course, it could in fact be that democratic change does not actually depend on public opinion of any sort at all but instead is an elite-driven phenomenon [see, e.g., @levitsky_how_2018].

@@

# Theme setup
theme_set(theme_minimal())
```

```{r data-input, include=FALSE, cache=TRUE}

@@

In analysis models, we have latent variables in both sides of equations, public suppport for democracy, democracy indices and corruption index (The latter one is included in APSR analyses).
Since measurement uncertainty associated with these latent variables can propagate into the inferences over coefficient parameters in models, we incorporate uncertainty by employing "Method of Composition" [@Tanner1993,p52], which has been applied in analyses with latent variables [@Treier2008;@caughey2018;@Kastellec2015].

As @caughey2018 explained, the main idea of MOC is to estimate the marginal distribution of coefficient parameter vector $\beta$, integrating over the uncertainty in latent variables $\theta$ (P A-15).
More explicitly, we wish to integrate the joint density of $\beta$ and $\theta$ over the distribution of $\theta$.
